Confronting preferential sampling in count and occupancy surveys: diagnosis and model-based triage \footnotemark[2]

### 2015-06-22 manuscript/pref_sampling.tex
Basic simulation structure in place but getting positive bias from TMB - some code included for contrasting different modeling approaches with simplified structure (e.g. no pref sampling via "spatial_only")

\begin{document}
\runningheads{P.~B.~Conn, D.~S.~Johnson, \& J.~T.~Thorson}{Preferential sampling in species distribution models}

@@

\title{Confronting preferential sampling in count and occupancy surveys: diagnosis and triage \footnotemark[2]}

>>>>

\begin{document}
\runningheads{P.~B.~Conn, J.~T.~Thorson, \& D.~S.~Johnson}{Preferential sampling in species distribution models}

@@

\title{Confronting preferential sampling in count and occupancy surveys: diagnosis and model-based triage \footnotemark[2]}
